High-Dimensional Regularized Discriminant Analysis

### 2013-05-11 reports/paper-hdrda.Rnw
Updated front matter to match AoAS format.

\documentclass[11pt]{article}
\usepackage{graphicx, amsmath, amssymb, bm, url, mathtools, natbib, amsthm, setspace}

\pagestyle{plain}
%----------------Page dimensions ----------------
\oddsidemargin 0.0in
\evensidemargin 0.0in
\topmargin -0.75in
\leftmargin 0in
\headheight 0.0in
\headsep 0.5in
%\footheight 0.0in
\footskip 0.5in
\footnotesep 0.0in
\textwidth 6.7in
\textheight 9.5in
%-----------Define Pictures---------------------
\def\picture #1 by #2 (#3){
   \vbox to #2{
        \hrule width #1 height 0pt depth 0pt
           \vfill
              \special{picture #3} % this is the low-level interface
                 }
    }
\def\scaledpicture #1 by #2 (#3 scaled #4){{
     \dimen0=#1 \dimen1=#2
      \divide\dimen0 by 1000 \multiply\dimen0 by #4
       \divide\dimen1 by 1000 \multiply\dimen1 by #4
        \picture \dimen0 by \dimen1 (#3 scaled #4)}
   }

\title{High-Dimensional Regularized Discriminant Analysis}

\author{John A. Ramey, Caleb K. Stein, and Dean M. Young}
%Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research
%  Center,\\ Seattle, Washington 98115, U.S.A. \email{johnramey@gmail.com}}
%\affil{Department of Statistical Science, Baylor University, Waco, Texas 76706, U.S.A. \email{Caleb\_Stein@baylor.edu} \email{Dean\_Young@baylor.edu}}

\newcommand{\xbar}{\bar{\bm x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}

\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}

\bibpunct{(}{)}{;}{a}{,}{,}

@@

\doublespacing

\maketitle

@@

\maketitle

@@

\bibliographystyle{plainnat}
\bibliography{rda}

>>>>

\documentclass[aoas,preprint]{imsart}

\usepackage{graphicx, amsmath, amssymb, bm, mathtools, amsthm}
\RequirePackage[OT1]{fontenc}
\RequirePackage{natbib}
\RequirePackage[colorlinks,citecolor=blue,urlcolor=blue]{hyperref}

% provide arXiv number if available:
%\arxiv{arXiv:0000.0000}

\startlocaldefs
\newcommand{\xbar}{\bar{\bm x}}
\newcommand{\tr}{\text{tr}}
\DeclareMathOperator*{\argmin}{arg\,min}
\DeclareMathOperator*{\argmax}{arg\,max}
\newtheorem{cor}{Corollary}
\newtheorem{lemma}{Lemma}
\newtheorem{proposition}{Proposition}
\newtheorem{thm}{Theorem}
\endlocaldefs

@@

\begin{frontmatter}

\title{High-Dimensional Regularized Discriminant Analysis}
\runtitle{High-Dimensional Regularized Discriminant Analysis}

\begin{aug}
\author{\fnms{John A.} \snm{Ramey}\thanksref{m1}\ead[label=e1]{johnramey@gmail.com}}
\author{\fnms{Caleb K.} \snm{Stein}\thanksref{m2}\ead[label=e2]{Caleb\_Stein@baylor.edu}}
\and
\author{\fnms{Dean M.} \snm{Young}\thanksref{m2}\ead[label=e3]{Dean\_Young@baylor.edu}}

\runauthor{J. A. Ramey et al.}

\affiliation{Fred Hutchinson Cancer Research Center\thanksmark{m1} and Baylor University\thanksmark{m2}}

\address{Vaccine and Infectious Disease Division\\
  Fred Hutchinson Cancer Research Center\\
  1100 Fairview Ave. N., M2-C200\\
  Seattle, Washington 98115, U.S.A.\\
  \printead{e1}}

\address{Department of Statistical Science\\
  Baylor University\\
  P.O. Box 97140\\
  Waco, Texas 76706, U.S.A.\\
  \printead{e2}\\
  \phantom{E-mail:\ }\printead*{e3}}
\end{aug}

%\begin{keyword}[class=AMS]
%\kwd[Primary ]{}
%\kwd{}
%\kwd[; secondary ]{}
%\end{keyword}

%\begin{keyword}
%\kwd{}
%\kwd{}
%\end{keyword}

\end{frontmatter}

% AOS,AOAS: If there are supplements please fill:
%\begin{supplement}[id=suppA]
%  \sname{Supplement A}
%  \stitle{Title}
%  \slink[doi]{10.1214/00-AOASXXXXSUPP}
%  \sdatatype{.pdf}" 
%  \sdescription{Some text}
%\end{supplement}

@@

@@

\bibliographystyle{imsart-nameyear}
\bibliography{rda}
